A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2023-04-29 papers/paper1/ms.tex
Updated environment, fleck, and tex files
Added Fleck to citations and tested fleck in the notebook

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.95\columnwidth]{Amplitude vs. Rotation for Kepler and TESS.png}
  \caption{Effect size for starspot contrast as seen in modulation amplitude versus period ($P_{\mathrm{rot}}$ [days]). The black points are the locus of spotted stars in the Kepler as measured by for late K dwarfs. The red points are the same stars, but measured with the TESS mission. The blue and green dashed lines represents the average amplitudes for all plotted stars for both Kepler and TESS, approximately 3.98\% and 6.94\%, respectively.}
\end{figure}
\FloatBarrier

@@

\software{
  pandas \citep{mckinney10, reback2020pandas},
  emcee \citep{foreman13},
  matplotlib \citep{hunter07},
  astroplan \citep{astroplan2018},
  astropy \citep{exoplanet:astropy13,exoplanet:astropy18},
  exoplanet \citep{exoplanet:exoplanet},
  numpy \citep{harris2020array},
  scipy \citep{jones01},
  ipython \citep{perez07},
  bokeh \citep{bokehcite},
  seaborn \citep{waskom14}}
%pytorch \citep{NEURIPS2019_9015}} % No pytorch yet!

>>>>

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=0.95\textwidth]{Amplitude vs. Rotation for Kepler and TESS.png}
  \caption{Effect size for starspot contrast as seen in modulation amplitude versus period ($P_{\mathrm{rot}}$ [days]). The black points are the locus of spotted stars in the Kepler as measured by for late K dwarfs. The red points are the same stars, but measured with the TESS mission. The blue and green dashed lines represents the average amplitudes for all plotted stars for both Kepler and TESS, approximately 3.98\% and 6.94\%, respectively.}
\end{figure*}
\FloatBarrier

@@

\software{
  astroplan \citep{astroplan2018},
  astropy \citep{exoplanet:astropy13,exoplanet:astropy18},
  bokeh \citep{bokehcite},
  emcee \citep{foreman13},
  exoplanet \citep{exoplanet:exoplanet},
  fleck \citep{fleckcite}
  ipython \citep{perez07},
  matplotlib \citep{hunter07},
  numpy \citep{harris2020array},
  pandas \citep{mckinney10, reback2020pandas},
  scipy \citep{jones01},
  seaborn \citep{waskom14}
}
%pytorch \citep{NEURIPS2019_9015}} % No pytorch yet!
